A performance assessment of evolutionary algorithms in volunteer computing environments

### 2016-10-30 EvoPar2017/paper.Rnw
Anonymising URLs. Closes #129

\title{A performance assessment of evolutionary algorithms in a
  volunteer computing system}

@@

In general, a distributed volunteer-based evolutionary computation
system based on the browser is simply a client-server system
which client is embedded in the browser via JavaScript. We call this
system {\sf NodIO}. All parts of the framework are free and available
with a free license from
\url{https://github.com/JJ/splash-volunteer}.

@@

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different JavaScript libraries, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, which should be running in
\url{http://nodio-jmerelo.rhcloud.com}, a free resource hosted in the
OpenShift Platform as a Service\footnote{It is not guaranteed to be running,
or running the same version, when you read this, however; you can always get
the sources from GitHub and set it up yourself.}.
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the proposed system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

@@

All these avenues of experimentation will be done openly following the
Open Science policy of our group, which, in fact, contributes to
establish trust and security between us and volunteers and is an
essential feature of the system. That is why this paper, as well as
the data and processing scripts, are published with a free license in GitHub at
\url{https://git.io/gecco-es-15}.

@@

This work has been supported in part by TIN2014-56494-C4-3-P (Spanish
Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio
2015 UGR). We are also grateful to {\tt @otisdriftwood} for his help
gathering users for the new experiments.

>>>>

\title{A performance assessment of evolutionary algorithms in
  volunteer computing environments}

@@

In general, a distributed volunteer-based evolutionary computation
system based on the browser is simply a client-server system
which client is embedded in the browser via JavaScript. We call this
system {\sf NodIO}. All parts of the framework are free and available
with a free license from \url{https://ANONYMOUS-URL}.
%\url{https://github.com/JJ/splash-volunteer}.

@@

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different JavaScript libraries, such as JQuery or {\tt
  Chart.js} have been used to build the user interface elements of the
framework, which should be running in \url{http://ANONYMOUS-URL}, 
%\url{http://nodio-jmerelo.rhcloud.com}, 
a free resource hosted in the
OpenShift Platform as a Service\footnote{It is not guaranteed to be running,
or running the same version, when you read this, however; you can always get
the sources from GitHub and set it up yourself.}.
%
\begin{figure}[!t]
\centering
\includegraphics[width=3in]{system.pdf}
\caption{Description of the proposed system. Clients execute a JavaScript EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one back from the server.}
\label{fig:system}
\end{figure}

@@

All these avenues of experimentation will be done openly following the
Open Science policy of our group, which, in fact, contributes to
establish trust and security between us and volunteers and is an
essential feature of the system. That is why this paper, as well as
the data and processing scripts, are published with a free license in GitHub at
\url{ANONYMOUS-URL}.
%\url{https://git.io/gecco-es-15}.

@@

%This work has been supported in part by TIN2014-56494-C4-3-P (Spanish
%Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio
%2015 UGR). We are also grateful to {\tt @otisdriftwood} for his help
%gathering users for the new experiments.
